iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-12 manuscript/main.tex
dropped a word to sneak the funding entirely in the second page. only references in 3rd page

A key feature of iSEE is the ability to dynamically transmit information between panels (Fig.~\ref{fig:iSEE}B).
Users can define arbitrary links between ``transmitting'' and ``receiving'' panels, whereby selections in transmitting tables and plots highlight the corresponding objects in receiving panels.
This facilitates exploration of the relationships between different aspects of the data -- for example, users can easily determine co-expression patterns of genes in a particular region of a reduced dimensionality embedding, by transmitting information from the reduced dimension plot to one or more feature expression plots.
The linking paradigm extends to multiple plots whereby a plot can transmit to multiple receivers, or a receiving plot can itself transmit to another plot.
This allows users to mimic the arbitrarily complex gating strategies often found in analyses of flow cytometry data \citep{finak2014opencyto}, with the advantage of being extensible to any (meta)data present in a SummarizedExperiment object.
Information can similarly be transferred between tables and plots, e.g., selecting a row determines how points are coloured in receiving plots.

@@

\section*{Acknowledgements}
We thank the organizers and participants of the European Bioconductor Meeting 2017, where the idea for this package was first conceived.
We also thank members of the Bioconductor community for their helpful suggestions.
\vspace*{-12pt}

>>>>

A key feature of iSEE is the ability to dynamically transmit information between panels (Fig.~\ref{fig:iSEE}B).
Users can define arbitrary links between ``transmitting'' and ``receiving'' panels, whereby selections in transmitting tables and plots highlight the corresponding data points in receiving panels.
This facilitates exploration of the relationships between different aspects of the data -- for example, users can easily determine co-expression patterns of genes in a particular region of a reduced dimensionality embedding, by transmitting information from the reduced dimension plot to one or more feature expression plots.
The linking paradigm extends to multiple plots whereby a plot can transmit to multiple receivers, or a receiving plot can itself transmit to another plot.
This allows users to mimic the arbitrarily complex gating strategies often found in analyses of flow cytometry data \citep{finak2014opencyto}, with the advantage of being extensible to any (meta)data present in a SummarizedExperiment object.
Information can similarly be transferred between tables and plots, e.g., selecting a row determines how points are coloured in receiving plots.

@@

\section*{Acknowledgements}
We thank organizers and participants at the European Bioconductor Meeting 2017, where the idea for this package was first conceived.
We also thank members of the Bioconductor community for helpful suggestions.
\vspace*{-12pt}
